Daily goals

### 2020-06-30 _TODO.Rmd
more intro
cleaning todo's

- [ ] intro: challenge in connecting different parts of the database with other databases that might refer to the same thing. For example taxon ids represent onw challenge in this sense, but it has been solved by the otol taxonomy project. Othe rchallenge is the study ids. This is not fully resolved yet by otol, but only partially by linking to the alignment repo.
- [ ] intro: programatic access.

>>>>

- [ ] ilex remote example started on Sun Jun 28 at 20:07:32 PDT 2020 and finished on Mon Jun 29 at 06:33:57 PDT 2020

- [ ] on methods, bootstrap summary part cite:
 SumTrees: Phylogenetic Tree Summarization Version 4.4.0, from DendroPy 4.4.0 (main-bc20409)

- [ ] intro: challenge in connecting different parts of the database with other databases that might refer to the same thing. For example taxon ids represent own challenge in this sense, but it has been solved by the otol taxonomy project. Othe rchallenge is the study ids. This is not fully resolved yet by otol, but only partially by linking to the alignment repo.
- [ ] intro: programatic access.
